Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-17 chapters/introduction/introduction.tex
calibration related work

\subsection{Geo-Calibration}
Automatic image geo-calibration continues to grow in importance as a
direct result of the increasing amount of imagery available
via the Internet. 
Solving this problem is of great value for a wide variety of fields,
with potential applications ranging from the forensic
sciences~\cite{stylianou13jane} to environmental
monitoring~\cite{zhang2012mining}.
Conceptually the geo-calibration task includes:
identifying the camera pose ({\em pose estimation}), the camera
geographic location ({\em geo-localization}), and the time the query
image was captured ({\em time estimation}).

@@

\item \textbf{Pose Estimation:}
\newline

\item \textbf{Geo-Localization:}
Extracting location-dependent or orientation-dependent features from
image data has drawn a great detail of attention from the vision
community~\cite{jacobs07geolocate, jacobs11geolocate,
jacobs08geoorient}. The common trend amongst these methods is that
they take advantage of a large dataset of geo-referenced images. Hays
and Efros~\cite{hays2008im2gps} use a data-driven scene matching
approach to localize a query image using a large dataset of geo-tagged
images.  Doersch \etal~\cite{doersch2012what} extract
location-dependent features that capture the relative appearance
differences of large cities.  Lin et al.~\cite{lin2013cross} localize
a ground-level image by learning the relationship between pairs of
ground and aerial images \footnote{In the context of our thesis, we
do not distinguish between the satellite imagery and the aerial
imagery} of the same location. Other techniques focus
on urban environments and infer location using local image
descriptors~\cite{schindler2008detecting,snavely2006photo}. Li et
al.~\cite{li2012worldwide} exploit geo-registered 3D points clouds to
estimate camera pose. Many other cues exist, such as the
skyline~\cite{baatz2012large,ramalingam2009geolocalization}, sky
appearance~\cite{lalonde2010sun,workman2014rainbow}, and
shadows~\cite{junejo2008estimating,wu2010geo}.
\newline

>>>>

\subsection{Geo-Calibration of Outdoor Images}
Automatic image geo-calibration of outdoor images continues to grow in
importance as a direct result of the increasing amount of imagery
available via the Internet.  Solving this problem is of great value
for a wide variety of fields, with potential applications ranging from
the forensic sciences~\cite{stylianou13jane} to environmental
monitoring~\cite{zhang2012mining}.  Conceptually the geo-calibration
task includes: identifying the camera pose ({\em pose estimation}),
the camera geographic location ({\em geo-localization}), and the time
the query image was captured ({\em time estimation}).

@@

\item \textbf{Pose Estimation:}
Li et al.~\cite{li2012worldwide} exploit geo-registered 3D points
clouds to estimate camera pose.
Vo \etal~\cite{vo2016localizing} propose a geo-localization network
that can regress the geo-orientation angle of the camera.
Agarwal \etal~\cite{agarwal2015metric} keep track of the camera pose
changes by matching SIFT~\cite{lowe1999object} feature points detected
between the input image and Google Street View panoramas.
%
The estimating of horizon line is an essential step for some pose
estimation algorithm, because horizon lines are closely related to
camera pitch and roll angles. If the camera focal length is known, one
can compute the camera pitch and roll angle from the horizon line.
Collins and Weiss~\cite{unitsphere1990} formulate horizon line
detection as a statistical estimation problem on the Gaussian Sphere,
which is similar to the geometry we use.  More recent work has
explored the use of dual space~\cite{alignment2014,dualspace2013}
representations. Among the clustering-based approaches, Xu et
al.~\cite{kitware2013} improve this pipeline by introducing a new
point-line consistency function that models errors in the line segment
extraction step.
\newline

\item \textbf{Geo-Localization:}
Extracting location-dependent features from
image data has drawn a great detail of attention from the vision
community~\cite{jacobs07geolocate, jacobs11geolocate,
jacobs08geoorient}. The common trend amongst these methods is that
they take advantage of a large dataset of geo-referenced images. Hays
and Efros~\cite{hays2008im2gps} use a data-driven scene matching
approach to localize a query image using a large dataset of geo-tagged
images.  Doersch \etal~\cite{doersch2012what} extract
location-dependent features that capture the relative appearance
differences of large cities.  Lin et al.~\cite{lin2013cross} localize
a ground-level image by learning the relationship between pairs of
ground and aerial images \footnote{In the context of our thesis, we
do not distinguish between the satellite imagery and the aerial
imagery} of the same location. Other techniques focus
on urban environments and infer location using local image
descriptors~\cite{schindler2008detecting,snavely2006photo}.
Many other cues exist, such as the
skyline~\cite{baatz2012large,ramalingam2009geolocalization}, sky
appearance~\cite{lalonde2010sun,workman2014rainbow}, and
shadows~\cite{junejo2008estimating,wu2010geo}.
\newline
